Predicting sales of newly published books

### 2015-08-12 paper.tex
Cambiado título y comentado abstract
cerrando issue #1
cerrando issue: Closes #1
Storing changes

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Using forecasting models for new book publishing}

@@

% Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
Many companies must face, as one of the most difficult tasks to accomplish, new product sales estimation, since in many cases no historical data to serve as guide is available.
Moreover, some of them lack the knowledge about forecasting methods and they can only make decisions based on the expert sales managers.
% Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
% Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose. Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda. En esos trabajos, cuando las ventas son estables, con una tendencia clara a lo largo del tiempo, los métodos clásicos son una buena opción. Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
In the literature, different methods of sales prediction, mainly for the fashion industry are proposed. 
In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
However, in the case of new products, such as a new book publishing, classical methods do not work properly.
% En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial. Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
In this paper, a rule-based decision method is proposed to address the problem of predicting the publishing roll. 
This method has been validated by the company that provided the data, as the obtained models provide information on the decision process and does not require human intervention, nor for the operation or for interpretation.
\end{abstract}

@@

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=som43.eps,width=\textwidth}
\caption{\small{Análisis de los datos iniciales, usando 43 variables descriptivas por libro, utilizando el SOM.}}
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analizyng the dataset with 13 descriptive inputs per book, and paying attention to the company experienced manager's recommendations, 7 inputs were considered; specifically, variables \emph{editorial} and \emph{materia} were included, while \emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total, numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total, semanas\_venta, tirada} were discarded. 
Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, taking into account the company experienced manager knowledge.

>>>>

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Predicting sales of newly published books}

@@

% Muchas empresas ven la estimación de las ventas de un nuevo producto como uno de las tareas más complicadas de llevar a cabo, ya que en muchos casos no suele haber datos históricos que sirvan de guía.
Many companies must face, as one of the most difficult tasks to accomplish, new product sales estimation, since in many cases no historical data to serve as guide is available. 
Moreover, some of them lack the knowledge about forecasting methods and they can only make decisions based on the expert sales managers.
% Es más, realizar predicciones poco precisas puede dar lugar a decisiones erróneas que resulten en un exceso de producción que no se llegue a vender o incluso a una producción deficitaria.
Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
% Es el caso del problema de la tirada editorial, en el que las empresas editoriales deben estimar el número de volúmenes a imprimir, siempre cuidando de no imprimir más de los que realmente acaben vendiéndose. Así pues, un sistema automático de predicción de ventas de libros para estimar la tirada editorial sería de gran ayuda para las empresas editoriales.
That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% En la bibliografía se proponen diferentes métodos de predicción de ventas, principalmente para la industria de la moda. En esos trabajos, cuando las ventas son estables, con una tendencia clara a lo largo del tiempo, los métodos clásicos son una buena opción. Sin embargo, en el caso de nuevos productos, tales como la publicación para su venta de un nuevo libro, los métodos clásicos no funcionan bien.
In the literature, different methods of sales prediction, mainly for the fashion industry are proposed. 
In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
However, in the case of new products, such as a new book publishing, classical methods do not work properly.
% En este trabajo se propone el uso de un método basado en reglas de decisión para abordar el problema de la predicción de la tirada editorial. Dicho método ha sido validado por la empresa que cedió los datos ya que ofrece información sobre el proceso de decisión y no necesita de intervención humana, ni para el funcionamiento ni para la interpretación.
In this paper, a rule-based decision method is proposed to address the
problem of predicting the publishing roll. 
% It's not proposed. It just obtained the best result with WEKA. 
This method has been validated by the company that provided the data, as the obtained models provide information on the decision process and does not require human intervention, nor for the operation or for interpretation.
\end{abstract}
%El abstract no me gusta nada. Debería ir a la introducción. Hay que
%enmarcar el problema (hace falta predecir las ventas para no imprimir
%más de la cuenta) hacer una resumen de lo hecho y decir el
%resultado. Lo más importante es, ¿cuál es el selling point?

@@

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
% datos serios de análisis estadístico de las variables.

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=som43.eps,width=\textwidth}
\caption{\small{Análisis de los datos iniciales, usando 43 variables
    descriptivas por libro, utilizando el SOM.}}
% Además, no es un análisis, es una evolución temporal de un solo
% entrenamiento.  - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analizyng the dataset with 13 descriptive inputs per
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{editorial} and \emph{materia} were included, while
\emph{devolucion\_total, reimpresiones, puntos\_vta1anio\_total,
  numero\_reimpresiones, devolucion1anio\_total, colocado1anio\_total,
  semanas\_venta, tirada} were discarded.  
% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
% ¿Análisis de varianza? - jj
Figure \ref{fig:som13} shows the initial analisys of dataset using the SOM on the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, taking into account the company experienced manager knowledge.
